% Guide de Survie du Doctorant (à Nantes)

\documentclass[12pt, english, squeezeCommittee, fancyChapter, fancyPart]{these-LUNAM}

%\usepackage{hyperref}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{ifthen}
\usepackage[strings]{underscore}
\usepackage{graphicx}
\usepackage[english, french]{babel}


%\usepackage{amsmath}  % Maths
%\usepackage{amsfonts} % Maths
%\usepackage{amssymb}  % Maths
%\usepackage{stmaryrd} % Maths (crochets doubles)

\usepackage{url}     % Mise en forme + liens pour URLs
\usepackage{array}   % Tableaux évolués
\usepackage{eurosym} % Symbole euro €

\usepackage{comment}

\usepackage[hmargin=3cm,vmargin=2.5cm]{geometry}

\begin{comment}
\usepackage{tikz}
\newdimen\pgfex
\newdimen\pgfem
\usetikzlibrary{arrows,shapes,shadows,scopes}
\usetikzlibrary{positioning}
\usetikzlibrary{matrix}
\usetikzlibrary{decorations.text}
\usetikzlibrary{decorations.pathmorphing}
\end{comment}

\usepackage[french=quotes]{csquotes}

% Commandes À FAIRE
\usepackage{color} % Couleurs du texte
\definecolor{darkred}{rgb}{0.5,0,0}
%\newcommand{\afaire}[1]{\textcolor{red}{[À FAIRE~: #1]}}
\newcommand{\trad}{\textcolor{blue}{\textbf{[Traduction à faire]}}\par}
\newcommand{\todo}[1]{\textcolor{red}{\textbf{[#1]}}}


% Id est
\newcommand{\ie}{\textit{i.e.} }

\usepackage{textcomp}
\geometry{inner=4.5cm, outer=2.5cm, top=2.5cm, bottom=2cm}

\RequirePackage[bookmarks,%
                colorlinks,%
                urlcolor=blue,%
                citecolor=blue,%
                linkcolor=blue,%
                hyperfigures,%
                pagebackref,%
                pdfcreator=LaTeX,%
                breaklinks=true,%
                pdfpagelayout=SinglePage,%
                bookmarksopen=true,%
                bookmarksopenlevel=2]{hyperref}


\title{Help for new PhD and Master students}
\subtitle{arriving on the campus of the \'Ecole Centrale de Nantes}
\author{AED}{PhD Students Association}{(AED)}

\discipline{PhD Association}

\specialty{Informative}

\institution{ECN} % - UN, UA, UM, ECN, EMN

\doctoralschool{498 (SPIGA) \& 503 (STIM)}
\laboratory{GeM, IRCCyN, LHEAA}
\thesisnumber{NaN}
\date{2012, December}

\reviewer{M.}{Lucas}{LETOURNEL}{PhD Student}{École Centrale de Nantes}
\reviewer{M.}{Mathieu}{FOCA}{PhD Student}{École Centrale de Nantes}

\examiner{M.}{Julien}{TANGUY}{PhD Student}{École Centrale de Nantes}

\supervisor{M.}{Maxime}{FOLSCHETTE}{PhD Student}{École Centrale de Nantes}

\cosupervisor{M.}{Raphaël}{POIRÉE}{PhD Student}{Université de Nantes}



\begin{document}
\maketitle

\tableofcontents

\frontmatter
\chapter*{Introduction}
Dear new PhD student,

You have now arrived at the campus of the prestigious École Centrale de Nantes as a PhD student! (Or maybe you're still sitting alone, in front of your computer, during your internship.)
But if you are reading this, you've already recieved your acceptance letters and are about to begin. //
We dont know who you are, where you come from, or whether or not what we have written here for you will be any use whatsoever. Who knows; maybe you already know everything about the school and its surroundings. We do know, however, that many of you will not know anything about the school, the life in the laboratories, Nantes, or even life in France when you arrive! For these students, we have put together this survival guide. It will introduce  you a little bit to the practical life in -- and outside of-- campus and give you some advice to navigate this new world you find yourself in! This guide is assembled by the Association des Étudiants en Doctorat (AED), an association dedicated to PhD students at Ecole Centrale de Nantes. If you have any input to improve this document, fell free to contact the AED by mail or by getting in touch with one of its officers directly!
Hoping to see you as soon as possible!


If you are looking for any help in your administrative stuff arriving in France, we strongly advise you to contact the organisation available here :\\
\url{http://www.nantes-chercheur.org}

\section*{The AED (Association des Étudiants en Doctorat) (PhD Students Association)}
\begin{foreigndisplayquote}{french}
\begin{small}
``Elle consume le temps, transformant son auteur en un être hybride, mi-étudiant, mi-adulte, coincé entre deux âges.
Elle dévore aussi l’espace, par l’empilement de livres, de fiches et de brouillons. Elle empiète sur la vie privée. Elle prend la tête.
''\footnote{The thesis takes time, changing its author into a hybrid creature, half-student, half-adult, stuck between two ages.
It also consumes space by stacking books, cards and drafts. It abrades the privacy. It gives headaches.}
\end{small}
\end{foreigndisplayquote}
%\url{http://www.scienceshumaines.com/la-solitude-du-thesard-de-fond_fr_27741.html}


And this, my friends, is why we must rise as one, united and powerful, against it! To this end, we have created an assoiation of PhD students on the campus of the École Centrale.

The Association of PhD Students of the École Centrale de Nantes (AED) aims to act on two distinct and complementary levels. First, on an academical level, it attempts to provide some useful information to Master and PhD students. Second, on a sociocultural level, it forms social ties between the current PhD students of the five laboratories of the École Centrale de Nantes. The AED hopes to
\begin{enumerate}
    \item Inform Master and engineering students about PhD and research,
    \item Inform PhD students about their future life as young researchers and about the École Centrale de Nantes and its organization. For instance, it seems important that all PhD students know that they have representatives at the councils of the school (see below).
    \item Gather together all PhD students for various social or cultural events. These events allow PhD students to meet and exchange ideas with students from other laboratories. Several events have already been held, including informal seminars and company visits (please refer to the news).
\end{enumerate}

For more information, please do not hesitate to contact the AED. (\url{aed@ec-nantes.fr})


During the year, we organize several activities :
\begin{itemize}
    \item PhD Conferences
    \item Billiards
    \item Karting
    \item Bolling
    \item \LaTeX{} courses
    \item BBQ
    \item Company visits/fairs (Airbus, DCNS, Peugeot-Citroën)
    \item Tree climbing
    \item Pub Crawls
\end{itemize}
\mainmatter

\input{parts/vie-sociale}

%\input{parts/nantes}

\input{parts/these}

\end{document}
